---
title: "Exercises Week 4"
author: "Felix Lennert"
date: "2020-11-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Assignment #3

## `dplyr`

Open the IMDb file.

1. Find the duplicated movie. How could you go across this? 
2. Which director has made the longest movie?
3. What's the highest ranked movie?
4. Which movie got the most votes?
5. Which movie had the biggest revenue in 2016?
6. How much revenue did the movies in the dataset make each year in total?
7. Filter movies following some conditions:
    a. More runtime than the average runtime (hint: you could also use `mutate()` before).
    b. Movies directed by J. J. Abrams.
    c. More votes than the median of all of the votes.
    d. The movies which have the most common value (the mode) in terms of rating (`mode()` does exist but will not work in the way you might like it to work -- run the script below and use the `my_mode` function).
    

```{r}
## helper function for mode

my_mode <- function(x){ 
    ta = table(x)
    tam = max(ta)
    if (all(ta == tam))
         mod = NA
    else
         if(is.numeric(x))
    mod = as.numeric(names(ta)[ta == tam])
    else
         mod = names(ta)[ta == tam]
    return(mod)
}

```

## `lubridate`

The following function gives you around 1000 of the latest tweets by Jean Claude Juncker's official Twitter account (you might consider storing them in a csv_file after downloading them).

```{r eval=FALSE, include=TRUE}
# install.packages("rtweet")
library(rtweet)
juncker_timeline <- get_timeline(user = "@JunckerEU", n = 1000)
```

Let's focus on the dates -- column name `created_at`.

1. Drop all other columns. Make new columns containing the day, month, year, and hour of the respective postings. 

2. Count the occurrences of years and months (in two different tibbles). Are there any patterns? Think about how you would visualize that (BONUS: try doing it using the basic code I have provided you in the last session). 

3. Round the dates down to the first day of the month. Why does this make more sense than just extracting the month? 

## `forcats`

For now, I will not include too many exercises in here. However, you will have to work with factors extensively when we come to data visualization.

Read in the file `ess2016_ger.csv`

1. Convert the variable `party_code` into a factor variable called `party_code_fct`. Drop all other variables.

2. Look at the distribution of the parties; keep the 4 most common ones, all others should be coded to `Other`. Do it using the following three functions. Which of them was the best for the job?
    a) using `fct_recode()`
    b) using `fct_collapse()`
    c) using `fct_lump()`
  
3. Reorder the factor levels according to their number of occurrence.

Assignment is due before our next session, i.e., 2020-12-02. You can hand it in group-wise on GRIPS.